\input{preamble.tex}

\begin{document}
{\Huge Hwang In Tak} \hfill

\vspace{0.5cm}

\textbf{Email}: sp301415@gmail.com \\
\textbf{Website}: \href{https://sp301415.com}{sp301415.com} \\

\cvsection{Research Interests}
Mathematical Cryptography \\

\cvsection{Education}
\textbf{Sangsan High School} \hfill 2015 --- 2017 \\
\\
\textbf{DGIST} \hfill 2018 --- 2022 \\
B.S. in School of Undergraduate Studies \hfill \textit{Summa Cum Laude} \\
\\
\textbf{UC Berkeley} \hfill 2018 Summer \\
Summer Sessions, in part of DGIST Freshmen Global Leadership Program (FGLP) \\
\\
\textbf{Seoul National University} \hfill 2023 --- Present \\
Integrated M.S./Ph.D. in Computer Science \& Engineering \\
Advisor: Prof. Yongsoo Song \\
\\

\cvsection{Honors and Scholarships}
\textbf{DGIST Dean's List} \hfill 2020 \\
\\
\textbf {CTF Security Competitions} \hfill 2020 --- Present \\
DEF CON CTF 2020 \hfill \textit{Finalist} \\
TokyoWesterns CTF 2020 Finals \hfill \textit{3rd place} \\
Midnight Sun CTF 2020 Finals \hfill \textit{7th place} \\
Real World CTF 2020/2021 (\href{https://www.boannews.com/media/view.asp?idx=94063}{Media Coverage})  \hfill \textit{1st place} \\
PlaidCTF 2021 \hfill \textit{5th place} \\
DEF CON CTF 2021 \hfill \textit{Finalist} \\
WhiteHat Contest 2021 \hfill \textit{3rd place} \\
SSTF Hacker's Playground \hfill \textit{5th place} \\

\cvsection{Research Experience}
\textbf{NIMS Academy for Industrial Mathematics} \hfill 2019.08. \\
I studied text-based modeling and big data mining, along with its use in industrial mathematics. \\
\\
\textbf{DGIST Computer Architecture and Systems Lab (CASLAB)} \hfill 2019.06. --- 2019.08. \\
Mentors: Prof. Dae Hoon Kim (DGIST)  \\
During intership, I studied various CPU Side Channel Attacks, such as Flush+Reload and Row Hammering. \\
\\
\textbf{DGIST Division of Intelligent Robotics} \hfill 2020.06. --- 2020.08. \\
Mentors: Dr. Sang Chul Lee (DGIST) \\
During internship, I studied algorithms for solving localization problems, i.e. determining the local position of autonomous robots. \\
\\
\textbf{DGIST Undergraduate Group Research Program (UGRP)}  \hfill 2020\\
Mentors: Prof. Hyo Sang Kang (DGIST) \\
I participated in two research teams as a part of UGRP. The topics were \textit{Developing Games with Multiple Genres} and \textit{Designing Surface Code with Uniform Hyperbolic Tiling}.  \\
For the former, I developed several games using Godot Engine. For the latter, I studied Quantum Error Correction, Hyperbolic Geometry and developed Uniform Hyperbolic Tiling Generator using Python. \\
\\
\textbf{DGIST Information and Intelligence Lab (IIL)}  \hfill 2022.01. --- 2022.06. \\
Mentors: Prof. Yong June Kim (DGIST) \\
During intership, I studied Privacy--Preserving Machine Learning(PPML) and Homomorphic Encryption. \\
\\
\textbf{SNU Cryptography \& Privacy Lab} (Internship) \hfill 2022.07. --- 2022.08. \\
Mentors: Prof. Yong Soo Song (SNU) \\
During Intership, I studied Homomorphic Encryption. I participated in a research about accelerating algorithms over Homomoprhic Encryption, and encryption itself. \\

\cvsection{Teaching Experience}
\textbf{Tutor at DGIST} \\
SE102 Multivariate Calculus \hfill 2019 Fall \\
SE201 Linear Algebra \hfill 2020 Spring \\
\\
\textbf{Teaching Assistant at KAIST PRE--URP} \\
Making a Quantum Error Correction Game \hfill 2020.12. --- 2021.02. \\
Drawing Escherian Image Using Hyperbolic Tiling \hfill 2021.06. --- 2021.08. \\
Decrypting RSA using Shor's Algorithm \hfill 2021.12. --- 2022.02. \\
\\
\textbf{Seminars at DGIST Clubs} \\
Solving Integer Problems Using Lattices \hfill 2021.11. \\
A Short Introduction to Approximation Theory \hfill 2022.04. \\
Game Development Using Godot Engine \hfill 2022.05. \\
Introduction to Homomorphic Encryption \hfill 2022.10. \\

\cvsection{Skills}
\textbf{Languages} \\
Korean (native), English (fluent) \\
\\
\textbf{Programming Languages} \\
Python (SageMath), Go, \LaTeX{}\\

\cvsection{Other Activities}
\textbf{Translator of elementaryOS} \hfill 2018 --- Present \\
I translated Several Parts of elementaryOS, most notably the main website, \href{https://elementary.io/ko/}{elementary.io}. \\
\\
\textbf{Member of CTF Team CodeRed} \hfill 2020 --- Present \\
I participate in CTF competitions from time to time, mostly solving crypto challenges. \\
\\
\textbf{Developer \& Writer of Team Invertible} \hfill 2020 --- Present \\
I am actively working on INVERTIBLE, a sokoban puzzle game. We recently ran our first closed beta test. We are planning to release the game on Steam in 2023. \\
\\
\textbf{President of DGIST Math Club} \hfill 2021 --- 2022 \\
I founded DGIST Math Club in 2021. We hold seminars and meetings on a regular basis. \\

\cvsection{Other Interests}
I love \href{https://letterboxd.com/sp301415/}{watching films}. I wrote and directed three short films in college, and I still write screenplays as a hobby!

\end{document}
